Topological Equivariant Artist Model

### 2022-03-28 slides/main.tex
artist
compiles through nu

\begin{frame}<presentation:1|handout:0>
    \frametitle{Domain specific libraries know their structure\cite{HeerSoftware2006}}
    \begin{table}
        %\renewcommand{\arraystretch}{2}
        %
        \begin{tabular}{>{\onslide<1->}l>{\onslide<2->}l>{\onslide<3->}l}
            \includegraphics[width=.24\textwidth]{figures/intro/table.png} & \includegraphics[width=.3\textwidth]{figures/intro/landsat.png} & \includegraphics[width=.33\textwidth]{figures/math/graph.png} \\
            ggplot\cite{wickhamGgplot2ElegantGraphics2016a}  & ImageJ\cite{schneiderNIHImageImageJ2012}& Gephi\cite{bastianGephiOpenSource2009}\\
            Vega\cite{satyanarayanDeclarativeInteractionDesign2014} & ImagePlot\cite{studiesCulturevisImageplot2021} & Graphviz\cite{ellsonGraphvizOpenSource2002}\\
            Altair\cite{vanderplasAltairInteractiveStatistical2018}& Napari\cite{nicholas_sofroniew_2021_4533308} & Networkx\cite{HagbergExploringNetwork2008}\\
             Tableau \cite{StoltePolaris2002}& &\\
            \cite{hanrahanVizQL2006,MackinlayShowme2007}&&\\        
        \end{tabular}
    \end{table}
\end{frame}

\begin{frame}<presentation:1|handout:0>
    \frametitle{General purpose libraries generally can't\cite{toryRethinkingVisualizationHighlevel2004}}
    \begin{figure}
        \includegraphics[height=.3\textheight]{../paper/figures/k_different_types.png}
    \end{figure}

@@

\subsubsection{Natural Transforms}
\begin{frame}<presentation:1-|handout:1>
    \frametitle{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \adjustbox{scale=3, center}{
        \begin{tikzcd}[ampersand replacement=\&]
            \& {} \arrow[dd, "\alpha" , Rightarrow, shorten=1.5em, color=nattran] \&             \\
          \textcolor{source}{\mathcal{C}} \arrow[rr, "F", bend left, color=functor, maps to] \arrow[rr, "G"', bend right, color=functor, maps to] \& \& \textcolor{target}{\mathcal{D}} \\
            \& {} \&            
          \end{tikzcd}}
\end{frame}

\begin{frame}<presentation:1-|handout:1>
    \frametitle{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]                      
        \end{tikzcd}
    \end{equation*}
\end{frame}

@@

            \onslide*<2,4|handout:2,4->{\opensetgc}

@@

\begin{frame}<presentation:1-|handout:1->
    \frametitle<0|handout:1>{Artist: $\vartistc: \sheafc_{\dbasec, \dtotalc} \rightarrow \sheafc_{\gbasec, \gtotalc}$}
    \frametitle<0|handout:2>{Data Space: $\vartistc_{\opensetc}: \sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \vindexpushc\sheafc_{\gbasec, \gtotalc}$}
    \frametitle<0|handout:3>{Display Space: $\vartist_{\opensetgc}: \vindexpullc\sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \sheafc_{\gbasec, \gtotalc}$}
    \frametitle<0|handout:4>{Artist: $\vartistc: \cgamma{\opensetc}{\dtotalc} \rightarrow \cgamma{\opensetgc}{\gtotalc}$}
    \onslide*<0|handout:1,4>{
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<0|handout:1>{\sheafc_{\gbasec, \g
          totalc}} 
          \onslide*<0|handout:4>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}}
          \onslide*<0|handout:1,4>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \& \& 
          \onslide*<0|handout:1>{\vindexpushc\sheafc_{\gbasec, \gtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetc}{\vindexpushc \gtotalc\restriction_{\opensetc}}}
          \\
          \& \& \\
          \onslide*<0|handout:1>{\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetgc}{\vindexpullc \dtotalc\restriction_{\opensetgc}}}
          \onslide*<0|handout:1,4>{\arrow[uu, "\vartistc_{\opensetgc}", color=artist, Rightarrow]}
          \&  \& 
          \onslide*<0|handout:1>{\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}}
          \onslide*<0|handout:1,4>{\arrow[ll, "\textcolor{functor}{\vindexpull}", color=functor]} 
          \onslide*<0|handout:1,4>{\arrow[uu, "\vartistc_{\opensetc}"', color=artist, Rightarrow]}
          \onslide*<4-|handout:1,4>{\arrow[lluu, "\vartistc"' description, dashed, color=artist, Rightarrow]}
        \end{tikzcd}
    \end{equation*}}

    \onslide*<1|handout:2>{
        \begin{equation*}
      \begin{tikzcd}[ampersand replacement =\&]
        \cgamma{\opensetc_1}{\dtotalc} 
        \arrow[dd, "\iota^*"', hook, color=set] 
        \arrow[rrrr, "\vartistc_{\opensetc_1}", bend left, color=artist, Rightarrow] \&  \& 
        \opensetc_1 
        \arrow[ll, "\sheafc_{\dbasec,\dtotalc}", color=sheaf, maps to] 
        \arrow[rr, "\sheafc_{\dbasec,\gtotalpushc}"', color=sheaf, maps to] \&  \& 
        \cgamma{\opensetc_1}{\gtotalpushc} 
        \arrow[dd, "\iota^*", hook', color=set] \\
        {} 
        \arrow[rrrr, dotted, color=artist,Rightarrow] \&\&\&\& {} \\
        \cgamma{\opensetc_2}{\dtotalc} 
        \arrow[rrrr, "\vartistc_{\opensetc_2}"', bend right, color=artist, Rightarrow] \&  \& 
        \opensetc_2 
        \arrow[ll, "\sheafc_{\dbasec,\dtotalc}"', color=sheaf, maps to] 
        \arrow[rr, "\sheafc_{\dbasec,\gtotalpushc}", color=sheaf, maps to] 
        \arrow[uu, "\iota" description, hook, color=base] \& \& 
        \cgamma{\opensetc_2}{\gtotalpushc}               
    \end{tikzcd}
        \end{equation*}}

    \onslide*<0|handout:3>{
        \begin{equation*}
    \begin{tikzcd}[ampersand replacement =\&]
    \cgamma{\opensetgc_1}{\dtotalpullc\restriction_{\opensetgc_1}} 
    \arrow[dd, "\iota^*"', hook, color=set] 
    \arrow[rrrr, "\vartistc_{\opensetgc_1}", bend left, color=artist, Rightarrow] \&  \& 
    \opensetgc_1 
    \arrow[ll, "\sheafc_{\gbasec, \dtotalpullc}", color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gbasec,\gtotalc}"', color=sheaf, maps to] \&  \& 
    \cgamma{\opensetgc_1}{\gtotalc\restriction_{\opensetgc_1}} 
    \arrow[dd, "\iota^*", hook', color=set] \\
    {} 
    \arrow[rrrr, dotted, color=artist, Rightarrow] \&\&\&\& {} \\
    \cgamma{\opensetgc_2}{\dtotalpullc\restriction_{\opensetgc_2}} 
    \arrow[rrrr, "\vartistc_{\opensetgc_2}"', bend right, color=artist, Rightarrow] \&  \& 
    \opensetgc_2 
    \arrow[ll, "\sheafc_{\gbasec,\dtotalpullc}"', color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gbasec, \gtotalc}", color=sheaf, maps to] 
    \arrow[uu, "\iota" description, hook, color=base] \& \& 
    \cgamma{\opensetgc_2}{\gtotalc\restriction_{\opensetgc_2}}   
    \end{tikzcd}
        \end{equation*}}    
    \onslide<0|handout:1>{
        \begin{equation*}
        \textcolor{nattran}{Nat}_{\opensetgc}(\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}, \sheafc_{\gbasec, \gtotalc}) = 
    \textcolor{nattran}{Nat}_{\opensetc}(\sheafc_{\dbasec, \dtotalc}, \textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc})
        \end{equation*}
    }
    \onslide<0|handout:4>{
        \begin{alertblock}{pull data section \dsectionc\ over graphic space $\gbasepointc \in \gbasec$}
            \begin{equation*}
                \vindexpullc\dsectionc(\gbasepointc) = \dsectionc(\vindexc(\gbasepointc)) = \dsectionc(\dbasepointc)
            \end{equation*}
        \end{alertblock}
        \begin{alertblock}{push graphic \gsectionc\ section over data space $\dbasepointc \in \dbasec$}
            \begin{equation*}
                \vindexpushc\gsectionc(\dbasepointc) = \gsectionc\restriction_{\vindexprec(\dbasepointc)} = \gsectionc(\gbasepointc) \forall \gbasepointc \in \vindexprec(\dbasepointc)
            \end{equation*}
        \end{alertblock}
        }
\end{frame}

@@

\begin{frame}<presentation:1|handout:1>{$\dfuncc = (\dfunchc, \dfunctc)$}
    \begin{tikzcd}[ampersand replacement = \&]
        \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
        \arrow[rr, "\dfuncpullc", color=action] 
        \&  \& 
        \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}} 
        \arrow[rr, "\dfunctc", color=action] 
        \&  \& 
        \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}} \\
        \&  \&  
        \&  \& \\
        \opensetc 
        \arrow[uu, "{\sheafc_{\dbasec, \dtotalc}}", maps to, color=sheaf]                 
        \&  \& 
        \opensetc^{\prime} 
        \arrow[ll, "\dfunchc", color=action] 
        \arrow[uu, "{\sheafc_{\dbasec, \dfuncpullc\dtotalc}}"', maps to, color=sheaf] 
        \arrow[rruu, "{\sheafc_{\dbasec, \dfuncpullc\dtotalc}}"', maps to, color=sheaf] 
        \&  \& 
    \end{tikzcd}
    \begin{description}
        \item[Base Transformation:] {$\dfunchc: \opensetc^{\prime} \rightarrow \opensetc$ where $\opensetc, \opensetc^{\prime} \subseteq \dbasec$, \\
        $\dfuncpullc\dsectionc\restriction_{\opensetc}: \dsectionc \mapsto \dsectionc\restriction_{\opensetc} \circ \dfunchc$}

        \item [Fiber Transformation:]{$\dfunctc: \dfuncpullc \dtotalc_{\dbasepointc^{\prime}} \rightarrow {\dfuncpullc\dtotalc_{\dbasepointc^{\prime}}} \in Hom(\dfuncpullc\dfiberc\restriction_{\dbasepointc}, \dfuncpullclllllll\dfiberc\restriction_{\dbasepointc}), \dbasepointc^{\prime} \in \opensetc^{\prime}$\\
        $\dfunctc: \dfuncpullc \dsectionc\restriction_{\opensetc} \mapsto \dfuncpullc \dsectionc^{\prime}\restriction_{\opensetc}$, $\dsectionc, \dsectionc^{\prime} \in \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}}$}
        \item [Section Transform:] $\dfuncc: \dsectionc\restriction_{\opensetc} \mapsto \dfuncpullc\dsectionc^{\prime}\restriction_{\opensetc}$
    \end{description}
\end{frame}

\begin{frame}<presentation:1|handout:1->
    \frametitle<presentation:1-|handout:1->{Combining Bundles}
    \frametitle<presentation:2|handout:2>{Transforming Combined Bundles: $\dfuncc = (\dfunchc, \prod\limits_{i=0}^{n}\dfunctc_i)$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, column sep=2ex]
                \onslide*<presentation:2|handout:2>{\dfunctc_0 \dfuncpullc} \dtotalc_0 
                \arrow[rdd, "\pi" description] 
                \onslide*<presentation:1|handout:1>{\arrow[r, "\cdot \otimes \cdot;", phantom]}
                \onslide*<presentation:2|handout:2>{\arrow[r, "\cdots \otimes \cdots", phantom]} 
                \& 
                \onslide*<presentation:2|handout:2>{\dfunctc_i \dfuncpullc} \dtotalc_i 
                \arrow[dd, "\pi" description] 
                \arrow[r, "\cdots \otimes \cdots", phantom] \& 
                \onslide*<presentation:2|handout:2>{\dfunctc_n \dfuncpullc} \dtotalc_n 
                \arrow[ldd, "\pi" description] \& = \& 
                \prod\limits_{i=0}^{n} 
                \onslide*<presentation:2|handout:2>{\dfunctc_i \dfuncpullc} \dtotalc_i 
                \arrow[dd, "\pi" description] \\    
                \&\&\&\&\\    
                \& 
                \onslide*<presentation:2|handout:2>{(\dfunchc=\dfunchc_{i \in [0,n]})}\dbasec 
                \& \& = \&        
                \onslide*<presentation:2|handout:2>{\dfunchc} \dbasec                                               
                \end{tikzcd}                                              
    \end{equation*}
    \onslide*<presentation:1|handout:1>{
        \begin{equation*}
            \prod\limits_{i=0}^{n} \underbrace{Hom(\dbasec,\dtotalc_i)}_{\dsectionc_i} = 
            \underbrace{Hom(\dbasec,  \prod\limits_{i=0}^{n}\dtotalc_i)}_{\dsectionc}
        \end{equation*}}
    \onslide*<presentation:2|handout:2>{
    \begin{equation*}
        \prod\limits_{i=0}^{n} \underbrace{Hom(\dfunchc\dbasec, \dfunctc_i\dfuncpullc \dtotalc_i)}_{\dfuncc_i\dsectionc_i} = 
        \underbrace{Hom(\dfunchc\dbasec,  \prod\limits_{i=0}^{n} \dfunctc_i\dfuncpullc\dtotalc_i)}_{\dfuncc\dsectionc}
    \end{equation*}}

@@

\begin{frame}<presentation:1|handout:1>{Equivariant Artist}
    $(\vartistc, \vartistc^{\prime})$ are equivariant with respect to $\dfuncc_{\dtotalc}$ if a compatible transform  $\dfuncc_{\gtotalc}$ can be defined such that 
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
        \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
        \arrow[rrr, "\vartistc", Rightarrow, color=artist] 
        \arrow[d, "\dfuncpullc_{\dtotalc}"', color=action] 
        \& \& \& 
        \imartist{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
        \arrow[d, "\dfuncpullc_{\gtotalc}", dotted] \\
        \cgamma{\opensetc^{\prime}}{\dfuncpullc_{\dtotalc}\dtotalc\restriction_{\opensetc^{\prime}}} 
        \arrow[dd, "\dfunctc_{\dtotalc}"', color=action] \& 
        \opensetc 
        \arrow[lu, dashed, maps to, color=sheaf] \& 
        \opensetgc 
        \arrow[l, "\vindexc"', color=functor] 
        \arrow[ru, dashed, maps to, color=sheaf] \& 
        \imartist{\opensetgc^{\prime}}{\dfuncpullc_{\gtotalc}\gtotalc\restriction_{\opensetgc^{\prime}}} 
        \arrow[dd, "\dfunctc_{\gtotalc}", dotted, color=action] \\
        \& 
        \opensetc^{\prime} 
        \arrow[u, "\dfunchc_{\dtotalc}", color=action] 
        \arrow[ld, dashed, maps to, color=sheaf] 
        \arrow[lu, dashed, maps to, color=sheaf] \& 
        \opensetgc^{\prime} 
        \arrow[l, "\vindexc"', color=functor] 
        \arrow[u, "\dfunchc_{\gtotalc}"', dotted, color=action] 
        \arrow[rd, dashed, maps to, color=sheaf] 
        \arrow[ru, dashed, maps to, color=sheaf] \& \\
        \cgamma{\opensetc^{\prime}}{\dtotalc^{\prime}\restriction_{\opensetc^{\prime}}} 
        \arrow[rrr, "\vartistc^{\prime}", Rightarrow, color=artist]  
        \& \& \& 
        \imartist{\opensetgc^{\prime}}{\gtotalc^{\prime}\restriction_{\opensetgc^{\prime}}}
        \end{tikzcd}
    \end{equation*}
    %$\vartistc^{\prime}(\dfunctc_{\dtotalc}(\dsectionc(\dfunchc_{\dtotalc}(\vindexc(\gbasepointc^{\prime}))))) = \dfunctc_{\gtotalc}(\vartistc(\dsectionc(\vindexc(\dfunchc_{\gtotalc}(\gbasepointc^{\prime})))))$
    %for all points $\gbasepointc^{\prime}\in \gbasec^{\prime}$
\end{frame}

@@

\begin{frame}<presentation:1|handout:1>{Components to Graphic}
    \begin{figure}
        \includegraphics[scale=.35]{../paper/figures/qhat.png}
    \end{figure}
\end{frame}
\end{document}

>>>>

\begin{frame}<presentation:1-|handout:1>
    \frametitle{Domain specific libraries know their structure\cite{HeerSoftware2006}}
    \begin{table}
        %\renewcommand{\arraystretch}{2}
        %
        \begin{tabular}{>{\onslide<1->}l>{\onslide<2->}l>{\onslide<3->}l}
            \includegraphics[width=.24\textwidth]{figures/intro/table.png} & \includegraphics[width=.3\textwidth]{figures/intro/landsat.png} & \includegraphics[width=.33\textwidth]{figures/math/graph.png} \\
            ggplot\cite{wickhamGgplot2ElegantGraphics2016a}  & ImageJ\cite{schneiderNIHImageImageJ2012}& Gephi\cite{bastianGephiOpenSource2009}\\
            Vega\cite{satyanarayanDeclarativeInteractionDesign2014} & ImagePlot\cite{studiesCulturevisImageplot2021} & Graphviz\cite{ellsonGraphvizOpenSource2002}\\
            Altair\cite{vanderplasAltairInteractiveStatistical2018}& Napari\cite{nicholas_sofroniew_2021_4533308} & Networkx\cite{HagbergExploringNetwork2008}\\
             Tableau \cite{StoltePolaris2002}& &\\
            \cite{hanrahanVizQL2006,MackinlayShowme2007}&&\\        
        \end{tabular}
    \end{table}
\end{frame}

\begin{frame}<presentation:1-|handout:1>
    \frametitle{General purpose libraries generally can't\cite{toryRethinkingVisualizationHighlevel2004}}
    \begin{figure}
        \includegraphics[height=.3\textheight]{../paper/figures/k_different_types.png}
    \end{figure}

@@

\subsubsection{Natural Transforms}
\begin{frame}<presentation:1-|handout:1>
    \frametitle{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \adjustbox{scale=3, center}{
        \begin{tikzcd}[ampersand replacement=\&]
            \& {} \arrow[dd, "\alpha" , Rightarrow, shorten=1.5em, color=nattran] \&             \\
          \textcolor{source}{\mathcal{C}} \arrow[rr, "F", bend left, color=functor] \arrow[rr, "G"', bend right, color=functor] \& \& \textcolor{target}{\mathcal{D}} \\
            \& {} \&            
          \end{tikzcd}}
\end{frame}

\begin{frame}<presentation:1-|handout:1>
    \frametitle{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]  
                \&  \& 
                \textcolor{target}{d_s} \& 
                \textcolor{source}{c} 
                \arrow[r, "G", maps to, color=functor] 
                \arrow[l, "F"', maps to, color=functor] \& 
                \textcolor{target}{d_t} \\
                \textcolor{source}{c_1} 
                \arrow[dd, "f" description, color=source] \& \& 
                \textcolor{target}{F(c_1)} 
                \arrow[dd, "F(f)"', color=target] 
                \arrow[rr, "\alpha_{c_1}", color=nattran] \& \& 
                \textcolor{target}{G(c_1)} 
                \arrow[dd, "G(f)", color=target] \\
                \& \& {} 
                \arrow[rr, "\alpha_{f}", dotted, color=nattran] \& \& {} \\
                \textcolor{source}{c_2} \& \& 
                \textcolor{target}{F(c_2)} 
                \arrow[rr, "\alpha{c_2}", color=nattran] \& \& 
                \textcolor{target}{G(c_2)} \\
                \& \& 
                \textcolor{target}{F} 
                \arrow[rr, "\alpha", Rightarrow, color=nattran] \& \& 
                \textcolor{target}{G}                        
        \end{tikzcd}                    
    \end{equation*}
\end{frame}

@@

            \onslide*<2,4-|handout:2,4->{\opensetgc}

@@

\begin{frame}<presentation:1-|handout:1->
    \frametitle<1|handout:1>{$\textcolor{homset}{Hom}_{\gbasec}(\sheaf_{\gbasec, \vindexpullc\dtotalc}, \sheaf_{\gbasec,\gtotalc}) = \textcolor{homset}{Hom}_{\dbasec}(\sheafc_{\dbasec, \dtotalc}, \sheafc_{\dbasec, \vindexpushc\gtotalc})$}
    \frametitle<2|handout:2>{Data Space: $\vartistc_{\dbasec}: \sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \sheafc_{\dbasec, \vindexpushc\gtotalc}$}
    \frametitle<3|handout:3>{Display Space: $\vartist_{\gbasec}: \sheafc_{\gbasec, \vindexpullc\dtotalc} \textcolor{artist}{\Rightarrow} \sheafc_{\gbasec, \gtotalc}$}
    \frametitle<4|handout:4>{Artist: $\vartistc: \dsectionc \mapsto \gsectionc$}

    \onslide*<1,4|handout:1,4>{
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<1|handout:1>{\sheafc_{\gbasec, \gtotalc}} 
          \onslide*<4|handout:4>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}}
          \onslide*<1,4|handout:1,4>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \& \& 
          \onslide*<1|handout:1>{\sheafc_{\dbasec, \vindexpushc\gtotalc}}
          \onslide*<4|handout:4>{\cgamma{\opensetc}{\vindexpushc \gtotalc\restriction_{\opensetc}}}
          \\
          \& \& \\
          \onslide*<1|handout:1>{\sheafc_{\gbasec, \vindexpullc\dtotalc}}
          \onslide*<4|handout:4>{\cgamma{\opensetgc}{\vindexpullc \dtotalc\restriction_{\opensetgc}}}
          \onslide*<1|handout:1>{\arrow[uu, "\vartistc_{\gbasec} \in \textcolor{homset}{Hom}_{\gbasec}", color=homset]}
          \onslide*<4|handout:4>{\arrow[uu, "\vartistc_{\gbasec}", color=artist]}
          \&  \& 
          \onslide*<1|handout:1>{\sheafc_{\dbasec, \dtotalc}}
          \onslide*<4|handout:4>{\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}}
          \onslide*<1,4|handout:1,4>{\arrow[ll, "\textcolor{functor}{\vindexpull}", color=functor]} 
          \onslide*<1|handout:1>{\arrow[uu, "\vartistc_{\dbasec} \in \textcolor{homset}{Hom}_{\dbasec}"', color=homset]}
          \onslide*<4|handout:4>{\arrow[uu, "\vartistc_{\dbasec}"', color=artist]}
          \onslide*<1|handout:1>{\arrow[lluu, "\vartistc \in \textcolor{homset}{Hom}_{\dbasec,\gbasec}"' description, dashed, color=homset]}
          \onslide*<4|handout:4>{\arrow[lluu, "\vartistc"' description, color=artist]}
        \end{tikzcd}
    \end{equation*}}

    \onslide*<2|handout:2>{
        \begin{equation*}
            \begin{tikzcd}[ampersand replacement=\&]  
                    \&  \& 
                    \sheafc_{\dbasec, \dtotalc} 
                    \arrow[rr, "\vartistc_{\dbasec}", Rightarrow, color=artist] \& \& 
                    \sheafc_{\dbasec, \vindexpushc\gtotalc}  \\
                    \opensetc_1\& \& 
                    \cgamma{\opensetc_1}{\dtotalc\restriction_{\opensetc_1}}
                    \arrow[dd, "\iota^*"', color=set] 
                    \arrow[rr, "\vartistc_{\opensetc_1}", color=artist] \& \& 
                    \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc_1}} 
                    \arrow[dd, "\iota^*", color=set] \\
                    \& \& {} 
                    \arrow[rr, "\vartistc_{\sheafc}", dotted, color=artist] \& \& {} \\
                    \arrow[uu, "\iota" description, hook, color=base] 
                    \opensetc_2 \& \& 
                    \cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}
                    \arrow[rr, "\vartistc_{\opensetc_2}", color=artist] \& \& 
                    \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc_2}} \\
                    \& \& 
                    \cgamma{\opensetc}{\dtotalc\restriction\opensetc} \& 
                    \opensetc 
                    \arrow[r, "\sheafc_{\dbasec,\vindexpushc\gtotalc}", maps to, color=sheaf] 
                    \arrow[l, "\sheafc_{\dbasec, \dtotalc}"', maps to, color=sheaf] \& 
                    \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction\opensetc}
            \end{tikzcd}                    
        \end{equation*}}

    \onslide*<3|handout:3>{
        \begin{equation*}
            \begin{tikzcd}[ampersand replacement=\&]  
                    \&  \& 
                    \sheafc_{\gbasec, \vindexpullc\dtotalc} 
                    \arrow[rr, "\vartistc_{\gbasec}", Rightarrow, color=artist] \& \& 
                    \sheafc_{\gbasec, \gtotalc}  \\
                    \opensetgc_1\& \& 
                    \cgamma{\opensetgc_1}{\vindexpullc\dtotalc\restriction_{\opensetgc_1}}
                    \arrow[dd, "\iota^*"', color=set] 
                    \arrow[rr, "\vartistc_{\opensetgc_1}", color=artist] \& \& 
                    \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc_1}} 
                    \arrow[dd, "\iota^*", color=set] \\
                    \& \& {} 
                    \arrow[rr, "\vartistc_{\sheafc}", dotted, color=artist] \& \& {} \\
                    \arrow[uu, "\iota" description, hook, color=base] 
                    \opensetc_2 \& \& 
                    \cgamma{\opensetgc_2}{\vindexpullc\dtotalc\restriction_{\opensetgc_2}}
                    \arrow[rr, "\vartistc_{\opensetgc_2}", color=artist] \& \& 
                    \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc_2}} \\
                    \& \& 
                    \cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction\opensetgc} \& 
                    \opensetgc 
                    \arrow[r, "\sheafc_{\gbasec,\gtotalc}", maps to, color=sheaf] 
                    \arrow[l, "\sheafc_{\gbasec, \vindexpullc\dtotalc}"', maps to, color=sheaf] \& 
                    \cgamma{\opensetc}{\gtotalc\restriction\opensetgc}
            \end{tikzcd}                    
        \end{equation*}
    }
    \onslide<4|handout:4>{
        \begin{alertblock}{pull data section \dsectionc\ over graphic space $\gbasepointc \in \gbasec$}
            \begin{equation*}
                \vindexpullc\dsectionc(\gbasepointc) = \dsectionc(\vindexc(\gbasepointc)) = \dsectionc(\dbasepointc)
            \end{equation*}
        \end{alertblock}
        \begin{alertblock}{push graphic \gsectionc\ section over data space $\dbasepointc \in \dbasec$}
            \begin{equation*}
                \vindexpushc\gsectionc(\dbasepointc) = \gsectionc\restriction_{\vindexprec(\dbasepointc)} = \gsectionc(\gbasepointc) \forall \gbasepointc \in \vindexprec(\dbasepointc)
            \end{equation*}
        \end{alertblock}
        }
\end{frame}

@@

\begin{frame}<presentation:1|handout:1>{$\dfuncc = (\dfunchc, \dfunctc)$}
    \begin{figure}
        \includegraphics[width=0.5\textwidth]{figures/math/dfunc.png}
    \end{figure}
    \begin{description}
        \item[Base Transformation:] {$\dfunchc: \opensetc^{\prime} \rightarrow \opensetc$ where $\opensetc, \opensetc^{\prime} \subseteq \dbasec$, \\
        $\dfuncpullc\dsectionc\restriction_{\opensetc}: \dsectionc \mapsto \dsectionc\restriction_{\opensetc} \circ \dfunchc$}

        \item [Fiber Transformation:]{$\dfunctc: \dfuncpullc \dtotalc_{\dbasepointc^{\prime}} \rightarrow {\dfuncpullc\dtotalc_{\dbasepointc^{\prime}}} \in Hom(\dfuncpullc\dfiberc\restriction_{\dbasepointc}, \dfuncpullc\dfiberc\restriction_{\dbasepointc}), \dbasepointc^{\prime} \in \opensetc^{\prime}$\\
        $\dfunctc: \dfuncpullc \dsectionc\restriction_{\opensetc} \mapsto \dfuncpullc \dsectionc^{\prime}\restriction_{\opensetc}$, $\dsectionc, \dsectionc^{\prime} \in \cgamma{\opensetc^{\prime}}{\dfuncpullc\dtotalc\restriction_{\opensetc^{\prime}}}$}
        \item [Section Transform:] $\dfuncc: \dsectionc\restriction_{\opensetc} \mapsto \dfuncpullc\dsectionc^{\prime}\restriction_{\opensetc}$
    \end{description}
\end{frame}

\begin{frame}<presentation:1|handout:1>{Equivariant Artist}
    $(\vartistc, \vartistc^{\prime})$ are equivariant with respect to $\dfuncc_{\dtotalc}$ if a compatible transform  $\dfuncc_{\gtotalc}$ can be defined such that 
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
        \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
        \arrow[rrr, "\vartistc", color=artist] 
        \arrow[d, "\dfuncpullc_{\dtotalc}"', color=action] 
        \& \& \& 
        \imartist{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
        \arrow[d, "\dfuncpullc_{\gtotalc}", dotted] \\
        \cgamma{\opensetc^{\prime}}{\dfuncpullc_{\dtotalc}\dtotalc\restriction_{\opensetc^{\prime}}} 
        \arrow[dd, "\dfunctc_{\dtotalc}"', color=action] \& 
        \opensetc 
         \& 
        \opensetgc 
        \arrow[l, "\vindexc"', color=functor] 
        \& 
        \imartist{\opensetgc^{\prime}}{\dfuncpullc_{\gtotalc}\gtotalc\restriction_{\opensetgc^{\prime}}} 
        \arrow[dd, "\dfunctc_{\gtotalc}", dotted, color=action] \\
        \& 
        \opensetc^{\prime} 
        \arrow[u, "\dfunchc_{\dtotalc}", color=action] 
        \& 
        \opensetgc^{\prime} 
        \arrow[l, "\vindexc"', color=functor] 
        \arrow[u, "\dfunchc_{\gtotalc}"', dotted, color=action] 
        \& \\
        \cgamma{\opensetc^{\prime}}{\dtotalc^{\prime}\restriction_{\opensetc^{\prime}}} 
        \arrow[rrr, "\vartistc^{\prime}", color=artist]  
        \& \& \& 
        \imartist{\opensetgc^{\prime}}{\gtotalc^{\prime}\restriction_{\opensetgc^{\prime}}}
        \end{tikzcd}
    \end{equation*}
    For all points $\gbasepointc^{\prime}\in \gbasec^{\prime}$:
    \begin{equation*}
        \vartistc^{\prime}(\dfunctc_{\dtotalc}(\dsectionc(\dfunchc_{\dtotalc}(\vindexc(\gbasepointc^{\prime}))))) = \dfunctc_{\gtotalc}(\vartistc(\dsectionc(\vindexc(\dfunchc_{\gtotalc}(\gbasepointc^{\prime})))))
    \end{equation*}

@@

@@

\begin{frame}<presentation:1|handout:1>{Components to Graphic}
    \begin{figure}
        \includegraphics[scale=.35]{../paper/figures/qhat.png}
    \end{figure}
\end{frame}
\end{comment}
\end{document}
